\textbf{Computational Fuzzy Extractors}

### 2013-03-25 trunk/CompFuzzExt.tex
Cleaning up proof of 3.5 and explanation of 5.3

We say that $\distLWE_{n, m, q, \chi}$ is $(\epsilon, t)$-secure if no (probabilistic) distinguisher running in time $t$ can distinguish the $\lwe$ instances from uniform except with probability $\epsilon$.
\end{definition}

@@

The $\distLWE$ with symbol fixing sources is implied by standard $\distLWE$~(proof in \secref{sec:proof of block theorem}).
%\vspace{.1in}
\begin{theorem}
\label{thm:blockLWE}
Let $n$ be a security parameter and define $q, m , \alpha = \poly(n)$.  Let $\beta  = \omega(1)$, and $W$ be a $m$-symbol fixing source over $\{0,1\}^{(m+\alpha)b}$ where $\Hoo(W) \geq mb$.  Then the $\distLWE_{n, m,q, W}$ assumption implies the $\distLWE_{n+\alpha+\beta, m+\alpha, q, W}$ w/ symbol fixing sources problem.
\end{theorem}
\bnote{Work on this writeup.}
We believe this statement is of independent interest.  It says that as long as there are security parameter more variables than equations no error we still get a secure $\LWE$ instance.  Intuitively, providing a single sample with no error should provide information should fix at most a single variable.  Thus, if there are significantly more variables than samples with no error, search $\LWE$ should still be hard.  We are able to show that $\distLWE$ is still hard.  In the reduction, we argue that the additional $\alpha+ \beta$ variables allow us to prepare a random block fixing instance even without knowing the values for the first $n$ variables.  The $\beta$ parameter is the slack needed to ensure that the ``free'' variables have influence on the last $\alpha$ samples.

@@

Let $n$ be a security parameter, $m ,q , \alpha= \poly(n)$.  Let $\beta = \omega(1)$.  All operations are computed $(\mod q)$ and we omit this notation.  
Let $\D$ be a distinguisher that breaks $\distLWE_{(m+\alpha), (n+\alpha+\beta), q, \chi'}$ where $\chi'_i = \chi_i$ for $i\leq m$ and $\chi_i \overset{d}= 0$ otherwise.  That is, $\D$ can distinguish $(m+\alpha)$ $\LWE$ instances from uniform over $n+\alpha+\beta$ variables where the last $\alpha$ equations have no error added.  We denote by $\vA$ be the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha+\beta)}$, $\vx$ be uniform over $\Fq^{(n+\alpha+\beta)}$, and $\ve= (e_1,..., e_{m+\alpha})$ where $e_1,..., e_m$ are generated from error distribution $\chi$ and $e_{m+i} =0$ for $i=1,..,\alpha$. Let $\epsilon \geq 1/\poly(n)$, then, 
\[
|\Pr[\D(\vA, \vA\vx+\ve) = 1] - \Pr[\D(\vA, \vu) =1]|> \epsilon.
\]
We build a distinguisher that breaks $\distLWE_{m, n, q, \chi}$.  Let $\vA'$ be uniform over $\Fq^{m\times n}$, $\vx'$ be uniform over $\Fq^n$ and $\ve'$ be drawn from $\chi^m$.  It suffices to build a distinguisher $\D'$ whose size at most \bnote{fill in} bigger than $\D$ where 
\begin{align}
\label{eq:block LWE dist}
|\Pr[\D'(\vA', \vA'\vx'+\ve') = 1] - \Pr[\D'(\vA', \vu) =1]|> (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon.
\end{align}
We will make a single call to $\D$ so we focus on how to prepare a random block fixing instance from the random instance we are given.  The code for $\D'$ is given in \figref{fig:perfectLWEreduction}.

\begin{figure}[t]
\begin{framed}
\begin{enumerate}
\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve$.
\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$.
\item Randomly generate $\vect{S} \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$.
\item If $\rank(\vect{S})<\alpha$, stop and output a random bit.
\item Find a set of $\alpha$ linearly independent columns.  Let  $T$ be the set of these indices.
\item Initialize $\vW \in \Fq^{n\times (\alpha+\beta)}$ to be the zero matrix.
\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
\item For all $x_i$ where $n\leq i$ and $i\not \in T$:\label{step:fill in matrix}
\subitem Generate $x_i\overset{\$}\leftarrow \Fq$.  
\subitem For $j=1,..., m$:
\subsubitem Generate $\vW_{j, i}\overset{\$}\leftarrow \Fq$
\subsubitem Set $b_j^* = b_j^* + \vW_{j, i} x_i$.
\item Initialize $\vA^*  = \left(\begin{array}{c | c}\vA' & \vW\\\hline \vR & \vS\end{array}\right)$.
\item \label{step:randomization}
For {$i=1,..., m$}:
\subitem Randomly generate $\gamma_i \leftarrow \Fq^{1\times \alpha}$.
\subitem Set $\va_{i} \leftarrow \va^*_{i}+\gamma_i (\vR||\vS)$
\subitem Set $b_i \leftarrow b^*_i + \gamma_i (b^*_{m+1},..., b^*_{m+k})$
\item Run $\D$ on input $\vA, \vb$.
\item Output $\D$'s output.
\end{enumerate}
\end{framed}
\caption{A PPT $\mathcal{D'}$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
\label{fig:perfectLWEreduction}
\end{figure}
The distinguisher $\mathcal{D'}$ has an advantage when $S$ is of rank $\alpha$.  This occurs with overwhelming probability~(techniques from Cooper~\cite{cooper2000rank}):
\begin{claim}
Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times \alpha+\beta}$ be randomly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \ngl(n)$.
\end{claim}
\begin{proof}
The probability that all $\alpha$ rows are linearly independent is the successive probability that each row is linearly independent of the previous rows, for the $i$th row this probability is $q^{i-1}/q^{\alpha+\beta}$.  By union bound, the probability that $\vS$ is not full rank is:
\begin{align*}
\Pr[\rank(\vS) < \alpha] &= \sum_{i=1}^{\alpha} \frac{q^{i-1}}{q^{\alpha+\beta}}
\leq \alpha \frac{q^{\alpha}}{q^{\beta+\alpha} }= \frac{\alpha}{q^{\beta}} = \ngl(n)\\
\end{align*}
Thus, $\Pr[\rank(\vS) = \alpha] \geq 1-\ngl(n)$.
\end{proof}
\begin{corollary}
$
|\Pr[\D(\vA, \vA\vx+\ve) = 1  | \rank(\vS) = \alpha] - \Pr[\D(\vA, \vu) =1 | \rank(\vS) = \alpha]|> \epsilon - \ngl(n).
$
\end{corollary}

We restrict analysis to the case where $\rank(\vS) = \alpha$.  
It suffices to show that $\D'$ properly prepares a random instance in this case.  We show this in three claims: 
\begin{enumerate}
\item If $\vA'$ is a random matrix then $\vA$ is a random matrix with $\rank(\vS) = \alpha$.
%\bnote{This should be if $\vb' | A$ is uniformly distributed, then $\vb |A $ is uniformly distributed.}
\item If $\vb' = \vA'\vx'+\ve'$ then $\exists \vx$~(uniformly distributed) where $\vb = \vA \vx + \ve'$ and where $\ve_i' = \ve_i$ for $1\leq i\leq m$ and $\ve_i' = 0$ otherwise.
\item If $\vb' | \vA'$ is uniformly distributed then $\vb | \vA$ is uniformly distributed.
\end{enumerate}

@@

A solution $\vx_T$ exists as $\vS_T$ is full rank and $\vx_T$ is uniformly distributed.

@@

We consider the product $(\vR|| \vS) \vx$.  It suffices to show that $(\vR|| \vS) \vx = (b_{m+1}^*,..., b_{m+\alpha}^*)$,

@@

\bnote{This needs to be checked.}
Let $\vb^*$ be the vector generated after step~\ref{step:fill in matrix}.  The only correlation between $\vb^*$ and $\vA^*$ is in the matrix $\vW$.  That is, for $1\leq i\leq n$, $b_i^* = b_i + \sum_{n<j \wedge j\not\in T} \vW_{i, j} x_j$, thus conditioning on $\vW$, $b_i^*$ is uniform assuming $b_i$ is uniform.  Thus $b^* | \vA^*$ is uniformly distributed.  Instead of showing that $\vb | \vA$ is uniformly distributed after step~\ref{step:randomization}, we show that $\vb |( \vA, \vA^*)$ is uniformly distributed.  Let $\vgamma$ represent the matrix formed by $\gamma_{i}$.

 The matrix $\vgamma$ is a deterministic function of $(\vA, \vA^*)$.  Thus, $\vb | (\vA, \vA^*) \overset{d}= \vb | (\vA, \vA^*, \vgamma)$.  The only dependence of $\vb$ on $(\vA, \vA^*, \vgamma)$ is in the matrix $\vgamma$.  Thus, $ \vb | (\vA, \vA^*, \vgamma) \overset{d}= \vb | \vgamma$. Recall that 
 \[
 \begin{pmatrix} b_{1}  \\ \vdots \\b_{m} \end{pmatrix}  = \begin{pmatrix} b_{1}^*  \\ \vdots \\b_{m}^* \end{pmatrix}  + \vgamma \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}
\]
Thus, $b_1,..., b_m $ are uniformly distributed conditioned on $\vgamma, b_{m+1}^*,..., b_{m+\alpha}^*$.  This completes the claim.
\end{proof}
Together Claims~\ref{cl:randomMatrixDist},~\ref{cl:random ax+e}, and~\ref{clm:random b} show that when $\rank(\vS) = \alpha$ the distinguisher $\D'$ properly prepares the instance thus, 
\begin{align*}
&\left|\Pr\left[\D'(\vA', \vu') = 1\right]- \Pr\left[\D'(\vA', \vb'=\vA'\vx + \ve)=1\right]  \right|\\
&\left|\Pr\left[\D'(\vA', \vu') = 1 | \rank(\vS) = \alpha \right]- \Pr\left[\D'(\vA', \vb'=\vA'\vx + \ve)=1 | \rank(\vS) = \alpha\right] \Pr[\rank(\vS) = \alpha] \right|\\
&\, =\left|\Pr\left[\D(\vA, \vu)=1 | \rank(S) =\alpha \right]- \Pr\left[\D(\vA, \vb)=1 | \rank(S) =\alpha \right]  \right| \Pr[\rank(\vS) = \alpha] \\
&\, \geq (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon
\end{align*}
Thus, Equation~(\ref{eq:block LWE dist}) is satisfied, this completes the proof.
\end{proof}
\section{Additional Proofs}

\subsection{Proof of \lemref{lem:averageToMaximalError}}
\label{sec:proof of average to maximal error}
\begin{proof}
Let $C$ be a distribution with $\Hoo(C)\geq k$ and let $C$ be a  $(t,\epsilon)$-average error Shannon code with recovery procedure $\rec$.  This implies that for all $t'\le t$
\[
\sum_{w\in W} \Pr[W=w]\Pr[ w'\leftarrow \sample (w, t') \wedge \rec(w') \neq w]\leq \epsilon.
\]
For $w$ denote by $\epsilon_w = \Pr[w'\leftarrow \sample(w, t') \wedge \rec(w') \neq w]$.  \bnote{There is something weird going on here.  The Markov inequality doesn't connect to what is below it.}Then by Markov inequality:
\[
\Pr_{w\in W}[ \epsilon_w \leq 2\expe_{w\leftarrow W} [\epsilon_w ] ] = \Pr_{w\in W} [\epsilon_w \le 2\epsilon ] \geq \frac{1}{2}
\]
Now suppose that for all $W'\subset W$ where $|W'|\geq 2^{k-1}$ there exists a $w\in W'$ such that $\Pr[ w'\leftarrow \sample (w,t') \wedge \rec(w') \neq w]> 2\epsilon$.  This implies that there exists a set $V$of size $V\geq |W|-2^{k-1}+1$ where $\forall v\in V, \epsilon_v >2\epsilon$.  Then note that $\Pr[W\in V]> 1/2$ as $W\setminus V$ contains at most $2^{k-1}-1$ points each of which has probability at most $1/2^k$ so $\Pr[W\in (W\setminus V)]\leq (2^{k-1}-1)/2^k < 1/2$.  Thus,
\begin{align*}
\Pr_{w\in W}[ w'\leftarrow \sample (w,t') \wedge \rec(w') \neq w]&\geq \sum_{w\in V}  \Pr[W=w]\Pr[ w'\leftarrow \sample (w,t') \wedge \rec(w') \neq w]\\
&\geq \sum_{w\in V} \Pr[W=w] 2\epsilon   = 2\epsilon \Pr[W\in V]> 2\epsilon\left(\frac{1}{2}\right)= \epsilon
\end{align*}
% where $\forall d\in D, \Pr[d'\leftarrow \sample(d) \wedge \rec(d') > 2\epsilon$.  In turn this implies that  
%\begin{align*}
%\Pr_{c\in C}[ c'\leftarrow \sample (c) \wedge \rec(c') \neq c]&=\frac{1}{|C|} \sum_{c\in C}  \Pr[ c'\leftarrow \sample (c) \wedge \rec(c') \neq c]\\
%&\geq \frac{1}{|C|} \sum_{d\in D}  \Pr[ d'\leftarrow \sample (d) \wedge \rec(d') \neq d]\\
%&\geq \frac{1}{|C|}\sum_{d\in D} 2\epsilon = \frac{1}{|C|}\left(\frac{|C|}{2}+1\right)2\epsilon = \epsilon + 2\epsilon/|C|> \epsilon
%\end{align*}
This is a contradiction.  The statement of~\lemref{lem:averageToMaximalError} follows directly.
\end{proof}

>>>>

We say that $\distLWE_{n, m, q, \chi}$ is $(\epsilon, t)$-secure if no (probabilistic) distinguisher running in time $t$ can distinguish the $\lwe$ instances from uniform except with probability $\epsilon$.  If $\distLWE_{n, m, q, \chi}$ is secure for all $t = \poly(n), \epsilon  = 1/\poly(n)$ we say it is \emph{secure}.
\end{definition}

@@

The $\distLWE$ with symbol fixing sources is implied by standard $\distLWE$.
%\vspace{.1in}
\begin{theorem}
\label{thm:blockLWE}
Let $n$ be a security parameter and define $q, m , \alpha = \poly(n)$.  Let $\beta  = \omega(1)$, and $W$ be a $m$-symbol fixing source over $\{0,1\}^{(m+\alpha)b}$ where $\Hoo(W) \geq mb$.  The $\distLWE_{n, m,q, W}$ assumption implies the $\distLWE_{n+\alpha+\beta, m+\alpha, q, W}$ w/ symbol fixing sources problem.
\end{theorem}
We believe this statement is of interest outside our setting.  \thref{thm:blockLWE} says that $\LWE$ is still secure when a small number of $\LWE$ samples have known error.  Roughly, we need the number of variables to be security parameter larger than the number of equations with known error.  Providing a single sample with no error ``fixes'' at most a single variable.  Thus, if there are significantly more variables than samples with no error, search $\LWE$ should still be hard.  We are able to show~(a stronger result) that $\distLWE$ is still hard.  In the reduction, we argue that the additional $\alpha+ \beta$ variables allow us to explain a random value for the last $\alpha$ samples without knowledge of the other variables.  The $\beta$ parameter is the slack needed to ensure that the ``free'' variables have influence on the last $\alpha$ samples.  A formal proof is in \secref{sec:proof of block theorem}.

@@

Let $n$ be a security parameter, $m ,q , \alpha= \poly(n)$.  Let $\beta = \omega(1)$.  All operations are computed $(\mod q)$ and we omit this notation.  
Let $\D$ be a distinguisher that breaks $\distLWE_{(m+\alpha), (n+\alpha+\beta), q, \chi'}$ where $\chi'_i = \chi_i$ for $i\leq m$ and $\chi_i \overset{d}= 0$ otherwise.  That is, $\D$ can distinguish $(m+\alpha)$ $\LWE$ instances from uniform over $n+\alpha+\beta$ variables where the last $\alpha$ equations have no error added.  We denote by $\vA$ be the uniform distribution over $\Fq^{(m+\alpha)\times(n+\alpha+\beta)}$, $\vx$ be uniform over $\Fq^{(n+\alpha+\beta)}$, and $\ve= (e_1,..., e_{m+\alpha})$ where $e_1,..., e_m$ are generated from error distribution $\chi$ and $e_{m+i} =0$ for $i=1,..,\alpha$. Let $\epsilon \geq 1/\poly(n)$, then, 
\[
|\Pr[\D(\vA, \vA\vx+\ve) = 1] - \Pr[\D(\vA, \vu) =1]|> \epsilon.
\]
We build a distinguisher that breaks $\distLWE_{m, n, q, \chi}$.  Let $\vA'$ be uniform over $\Fq^{m\times n}$, $\vx'$ be uniform over $\Fq^n$ and $\ve'$ be drawn from $\chi^m$.  It suffices to build a ppt distinguisher $\D'$  where 
\begin{align}
\label{eq:block LWE dist}
|\Pr[\D'(\vA', \vA'\vx'+\ve') = 1] - \Pr[\D'(\vA', \vu) =1]|> (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon.
\end{align}
We will make a single call to $\D$ so we focus on how to prepare a random block fixing instance from the random instance we are given.  The code for $\D'$ is given in \figref{fig:perfectLWEreduction}.

\begin{figure}[t]
\begin{framed}
\begin{enumerate}
\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve$.
\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$. Initialize $\vW \in \Fq^{n\times (\alpha+\beta)}$ to be the zero matrix.
\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
\item Randomly generate $\vect{S} \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$.
		\subitem If $\rank(\vect{S})<\alpha$, stop and output a random bit.
\item Find a set of $\alpha$ linearly independent columns in $\vS$.  Let $T$ be the set of these indices.
\item For all $x_i$ where $n\leq i$ and $i\not \in T$:\label{step:fill in matrix}
\subitem Generate $x_i\overset{\$}\leftarrow \Fq$.  
\subitem For $j=1,..., m$:
\subsubitem Generate $\vW_{j, i}\overset{\$}\leftarrow \Fq$
\subsubitem Set $b_j^* = b_j^* + \vW_{j, i} x_i$.
\item Initialize $\vA^*  = \left(\begin{array}{c | c}\vA' & \vW\\\hline \vR & \vS\end{array}\right)$.
\item \label{step:randomization}
For {$i=1,..., m$}:
\subitem Randomly generate $\gamma_i \leftarrow \Fq^{1 \times \alpha}$.
\subitem Set $\va_{i} \leftarrow \va^*_{i}+\gamma_i (\vR||\vS)$
\subitem Set $b_i \leftarrow b^*_i + \gamma_i (b^*_{m+1},..., b^*_{m+k})$
\item Run $\D$ on input $\vA, \vb$.
\item Output $\D$'s output.
\end{enumerate}
\end{framed}
\caption{A PPT $\mathcal{D'}$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
\label{fig:perfectLWEreduction}
\end{figure}
The distinguisher $\mathcal{D'}$ has an advantage when $S$ is of rank $\alpha$.  This occurs with overwhelming probability~(techniques from Cooper~\cite{cooper2000rank}):
\begin{claim}
Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be randomly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \ngl(n)$.
\end{claim}
\begin{proof}
The probability that all $\alpha$ rows are linearly independent is the successive probability that each row is linearly independent of the previous rows, for the $i$th row this probability is $q^{i-1}/q^{\alpha+\beta}$.  By union bound and $\beta = \omega(1)$, the probability that $\vS$ is not full rank is:
\begin{align*}
\Pr[\rank(\vS) < \alpha] &= \sum_{i=1}^{\alpha} \frac{q^{i-1}}{q^{\alpha+\beta}}
\leq \alpha \frac{q^{\alpha}}{q^{\alpha+\beta} }=\ngl(n)\\
\end{align*}
Thus, $\Pr[\rank(\vS) = \alpha] \geq 1-\ngl(n)$.
\end{proof}
\begin{corollary}
$
|\Pr[\D(\vA, \vA\vx+\ve) = 1  | \rank(\vS) = \alpha] - \Pr[\D(\vA, \vu) =1 | \rank(\vS) = \alpha]|> \epsilon - \ngl(n).
$
\end{corollary}

We are interested in the case where $\rank(\vS) = \alpha$, and it suffices to show that $\D'$ prepares a random instance in this case. We show this in the following three claims: 
\begin{enumerate}
\item If $\vA'$ is a random matrix then $\vA$ is a random matrix with $\rank(\vS) = \alpha$.
%\bnote{This should be if $\vb' | A$ is uniformly distributed, then $\vb |A $ is uniformly distributed.}
\item If $\vb' = \vA'\vx'+\ve'$ then $\exists \vx$~(uniformly distributed) where $\vb = \vA \vx + \ve'$ and where $\ve_i' = \ve_i$ for $1\leq i\leq m$ and $\ve_i' = 0$ otherwise.
\item If $\vb' | \vA'$ is uniformly distributed then $\vb | \vA$ is uniformly distributed.
\end{enumerate}

@@

A solution $\vx_T$ exists as $\vS_T$ is full rank and furthermore, $\vx_T$ is uniformly distributed.

@@

Recall that $b_i =b_i^* + \gamma_i(b_{m+1}^*,..., b_{m+k}^*)$.  We consider the product $(\vR|| \vS) \vx$.  It suffices to show that $(\vR|| \vS) \vx = (b_{m+1}^*,..., b_{m+\alpha}^*)$,

@@

Let $\vb^*$ be the vector generated after step~\ref{step:fill in matrix}.  The only correlation between $\vb^*$ and $\vA^*$ is in the matrix $\vW$, i.e. for $1\leq i\leq n$, $b_i^* = b_i + \sum_{n<j \wedge j\not\in T} \vW_{i, j} x_j$, thus conditioning on $\vW$, $b_i^*$ is uniform assuming $b_i$ is uniform.  Thus $\vb^* | \vA^*$ is uniformly distributed. We show that $\vb |( \vA, \vA^*)$ is uniformly distributed, therefore, showing that $\vb | \vA$ is uniformly distributed after step~\ref{step:randomization}.  Let $\vgamma$ represent the matrix formed by $\gamma_{i}$.

 The matrix $\vgamma$ is a deterministic function of $(\vA, \vA^*)$.  Thus, $\vb | (\vA, \vA^*) \overset{d}= \vb | (\vA, \vA^*, \vgamma)$.  The only dependence of $\vb$ on $(\vA, \vA^*, \vgamma)$ is in the matrix $\vgamma$.  Thus, $ \vb | (\vA, \vA^*, \vgamma) \overset{d}= \vb | \vgamma$. Recall that 
 \[
 \begin{pmatrix} b_{1}  \\ \vdots \\b_{m} \end{pmatrix}  = \begin{pmatrix} b_{1}^*  \\ \vdots \\b_{m}^* \end{pmatrix}  + \vgamma \begin{pmatrix} b_{m+1}^*  \\ \vdots \\b_{m+\alpha}^* \end{pmatrix}
\]
Thus, $b_1,..., b_m $ are uniformly distributed conditioned on $\vgamma, b_{m+1}^*,..., b_{m+\alpha}^*$.  This completes the claim.
\end{proof}

Finally, the reduction runs in polynomial time and together Claims~\ref{cl:randomMatrixDist},~\ref{cl:random ax+e}, and~\ref{clm:random b} show that when $\rank(\vS) = \alpha$ the distinguisher $\D'$ properly prepares the instance thus, 
\begin{align*}
&\left|\Pr\left[\D'(\vA', \vu') = 1\right]- \Pr\left[\D'(\vA', \vb'=\vA'\vx + \ve)=1\right]  \right|\\
&\, = \left| \Pr\left[\D'(\vA', \vu') = 1 | \rank(\vS) = \alpha \right]- \Pr\left[\D'(\vA', \vb'=\vA'\vx + \ve)=1 | \rank(\vS) = \alpha\right]\right| \Pr[\rank(\vS) = \alpha] \\
&\, =\left|\Pr\left[\D(\vA, \vu)=1 | \rank(S) =\alpha \right]- \Pr\left[\D(\vA, \vb)=1 | \rank(S) =\alpha \right]  \right| \Pr[\rank(\vS) = \alpha] \\
&\, \geq (\epsilon - \ngl(n))(1-\ngl(n)) \approx \epsilon
\end{align*}
Thus, Equation~(\ref{eq:block LWE dist}) is satisfied, this completes the proof.
\end{proof}
\section{Additional Proofs}

\subsection{Proof of \lemref{lem:averageToMaximalError}}
\label{sec:proof of average to maximal error}
\begin{proof}
Let $C$ be a distribution with $\Hoo(C)\geq k$ and let $C$ be a  $(t,\epsilon)$-average error Shannon code with recovery procedure $\rec$.  This implies that for all $t'\le t$
\[
\sum_{c\in C} \Pr[C=c]\Pr[ c'\leftarrow \sample (c, t') \wedge \rec(c') \neq c]\leq \epsilon.
\]
For $c$ denote by $\epsilon_c = \Pr[c'\leftarrow \sample(c, t') \wedge \rec(c') \neq c]$.  
Then by Markov inequality:
\[
\Pr_{c\in C}[ \epsilon_c \leq 2\expe_{c\leftarrow C} [\epsilon_c ] ] = \Pr_{c\in C} [\epsilon_c \le 2\epsilon ] \geq \frac{1}{2}
\]
Let $C'$ denote the of  set all $c\in C$ where $\epsilon_c\leq 2\epsilon$.  Note that $\Pr_{c\leftarrow C}[c\in C']\geq 1/2$.  Since $H_\infty(C)\geq k, |C'|\geq 2^{k-1}$~(otherwise $C'$ would contain total weight less that $2^{k-1}\frac{1}{2^k} = 1/2$).  This completes the proof of the~\lemref{lem:averageToMaximalError}.

%Suppose that for all $W'\subset W$ where $|W'|\geq 2^{k-1}$ there exists a $w\in W'$ such that $\Pr[ w'\leftarrow \sample (w,t') \wedge \rec(w') \neq w]> 2\epsilon$.  
%This implies that there exists a set $V$of size $V\geq |W|-2^{k-1}+1$ where $\forall v\in V, \epsilon_v >2\epsilon$.  Then note that $\Pr[W\in V]> 1/2$ as $W\setminus V$ contains at most $2^{k-1}-1$ points each of which has probability at most $1/2^k$ so $\Pr[W\in (W\setminus V)]\leq (2^{k-1}-1)/2^k < 1/2$.  Thus,
%\begin{align*}
%\Pr_{w\in W}[ w'\leftarrow \sample (w,t') \wedge \rec(w') \neq w]&\geq \sum_{w\in V}  \Pr[W=w]\Pr[ w'\leftarrow \sample (w,t') \wedge \rec(w') \neq w]\\
%&\geq \sum_{w\in V} \Pr[W=w] 2\epsilon   = 2\epsilon \Pr[W\in V]> 2\epsilon\left(\frac{1}{2}\right)= \epsilon
%\end{align*}
%% where $\forall d\in D, \Pr[d'\leftarrow \sample(d) \wedge \rec(d') > 2\epsilon$.  In turn this implies that  
%%\begin{align*}
%%\Pr_{c\in C}[ c'\leftarrow \sample (c) \wedge \rec(c') \neq c]&=\frac{1}{|C|} \sum_{c\in C}  \Pr[ c'\leftarrow \sample (c) \wedge \rec(c') \neq c]\\
%%&\geq \frac{1}{|C|} \sum_{d\in D}  \Pr[ d'\leftarrow \sample (d) \wedge \rec(d') \neq d]\\
%%&\geq \frac{1}{|C|}\sum_{d\in D} 2\epsilon = \frac{1}{|C|}\left(\frac{|C|}{2}+1\right)2\epsilon = \epsilon + 2\epsilon/|C|> \epsilon
%%\end{align*}
%This is a contradiction.  The statement of~\lemref{lem:averageToMaximalError} follows directly.
\end{proof}
